---
title: "batch.run.1.R"
author: "Anna Talucci"
date: "2023-02-22"
output: html_document
---
#**Moved over to separate repository

# batch.run1.R
# Change Log
#    September 2014 
#       Added user flag to allow switching between Sandy's settings and Ethan's
#       Added "swi.grd" and "swi.gri" to list of metrics.

## process the first set of dems for Canada
# This script manages calculation of multiple terrain metrics on 
# many grids.
# I've put three comment character (###) on lines that might need to be changed.
#  Additionally the file "grids.csv"  should be updated to include the names
#  of all your grids.  Only the "grid" column in that file is used by R.
## made a text file of just the dem base name instead. SH

```{r}
rm(list=ls()) ### (you may not want this line) clear workspace   CAUTION!!!
```

# Setup

```{r}
user <- "anna"  # or sandy  this controls machine specific configuration
stopifnot(user %in% c("anna", "sandy"))
```

```{r}
if(user == "anna"){
  input.dir <- "../data/dems/"   ###  Where your grids are
  output.dir <- "../outputs/" ###  Where the results should be put
  rsaga.path <- "C:/Program Files (x86)/SAGA-GIS-2-1-0"
}
```

```{r}
if(user == "sandy"){
  setwd("c:/rfiles/fires/terrain/launch/")   ### Change to wherever you put the code files sourced below
  # Setup Paths
  workspace <- "c:/data/fires/canada/terrain/temp1/"   ### If running multiple processes make sure that each uses it's own workspace
  # Also, I'm not currently cleaning this out.  You will want to delete it once in a while.
  input.dir <- "c:/data/fires/canada/demsall/"   ###  Where your grids are
  output.dir <- "c:/data/fires/canada/terrain/out1/" ###  Where the results should be put
  rsaga.path <- "C:/Program Files (x86)/SAGA-GIS"  ### MUST GET THIS RIGHT! You will know...
  
}
```

```{r}
source("terrain.function.calls.R")
source("run.metric.R")
```

```{r}
startover <- FALSE  #  If FALSE then grids which have all of the expected metrics will be skipped.
                    # If TRUE then everything will be run regardless of pre-existing output.
```

# Read in calls file (Should not be changed at all)
```{r}
calls <- read.csv("../data/callsGirds/calls.csv", stringsAsFactors=FALSE)
```

# Read in grids file (you'll need to update this to include all the grids you want to run)
```{r}
grids <- as.vector(scan("demlist1.txt", what="character"))
```


# This is a list of all the metrics expected from the current call file.
```{r}
all.metrics <- c("hydro_carea.grd", "hydro_carea.gri", "hydro_caspect.grd", 
                 "hydro_caspect.gri", "hydro_cflowpath.grd", "hydro_cflowpath.gri", 
                 "hydro_cheight.grd", "hydro_cheight.gri", "hydro_cslope.grd", 
                 "hydro_cslope.gri", "morpho_aspect.grd", "morpho_aspect.gri", 
                 "morpho_curv.grd", "morpho_curv.gri", "morpho_hcurv.grd", "morpho_hcurv.gri", 
                 "morpho_slope.grd", "morpho_slope.gri", "morpho_vcurv.grd", "morpho_vcurv.gri", 
                 "relpos.grd", "relpos.gri", "tci.grd", "tci.gri", "ws0.grd", 
                 "ws0.gri", "ws135.grd", "ws135.gri", "ws180.grd", "ws180.gri", 
                 "ws225.grd", "ws225.gri", "ws270.grd", "ws270.gri", "ws315.grd", 
                 "ws315.gri", "ws45.grd", "ws45.gri", "ws90.grd", "ws90.gri", "swi.grd", "swi.gri")
```


## This code was used to create the list above after running a single grid ("blake30")
# l <- list.files(output.dir, pattern="blake30", ignore.case = TRUE)
# all.metrics <- gsub("blake30_", "", l, fixed=FALSE, ignore.case = TRUE )
# dput(all.metrics)

# Set up RSAGA environment
```{r}
library(RSAGA)
```

```{r}
env <- rsaga.env(path=rsaga.path) 
```

# Loop through grids 
```{r}
for(i in 1:length(grids)){
  grid <- grids[i]  
  # grid <- "blake30"  # for testing
  cat("\n\nStarting grid", i, "of", length(grids), "\t", grid, "\n\n")
```  
  ## skip completed grids if appropriate
```{r}  
  if(!startover){ 
    result.files <- paste(output.dir, grid, "_", all.metrics, sep="")
    if(all(file.exists(result.files))) next
  }
```  
  # Run all the metrics for the grid
```{r}  
for(run in calls$run){
    run.metric(grid=grid, 
               run=run, 
               calls=calls, 
               input.dir=input.dir, 
               output.dir=output.dir,
               workspace=workspace, 
               env=env) 
  }
}
```

**THE END**