---
title: "FAB DEM Mosaic"
author: "Anna Talucci"
date: "2023-03-10"
output: html_document
---

# Overview

Combine DEM tiles for study areas

SK field sites latitude and longitude range from FAB DEM from Compernicus (bare earth)

Lat long range for SK
Latitude (N)
[1] 53.1911
[1] 57.3646

Longitude (W)
[1] -111.3801
[1] -88.612

Lat long range for NWT
Latitude (N)
[1] 60.2151
[1] 64.1714

Longitude (W)
[1] -121.0111
[1] -113.0163

# Packages 

```{r}
library(terra)
library(gdalUtilities)
library(sf)
library(ggspatial)
```


# Data

## Points
```{r}
pts = st_read("../data/FieldPoints/Field1983-2016/AllPointsEA1983-2016.shp", "AllPointsEA1983-2016") 
```

## Filter for groups 2

```{r}
( ss1 = pts %>% filter(group2 =="ss1") )
ss2 = pts %>% filter(group2 =="ss2")
ssbp1 = pts %>% filter(group2 =="ssbp1")
ssbp2 = pts %>% filter(group2 =="ssbp2")
ts1 = pts %>% filter(group2 =="ts1")
tstp1 = pts %>% filter(group2 =="tstp1")
tp1 = pts %>% filter(group2 =="tp1")
tp2 = pts %>% filter(group2 =="tp2")
tp3 = pts %>% filter(group2 =="tp3")
```


## Look at 1st and last sk raster
```{r}
first<-rast("../data/DEMs/DEMFieldSK/N53W088_FABDEM_V1-0.tif")
last<-rast("../data/DEMs/DEMFieldSK/N57W112_FABDEM_V1-0.tif")
```

```{r}
first
```

```{r}
last
```

# Projections
```{r}
projection<-crs(last)
projection
```

# Masaic with Terra 

## Yukon 
### Make list of rasters
```{r}
yk_rlist <- list.files(path ="../data/DEMs/DEMFieldYK/",pattern = ".tif$",full.names = TRUE )
```

### Define as rasters
```{r}
yk_r <- lapply(yk_rlist,   rast)
```

###  Make a spatial raster collection
```{r}
yk_rsrc <- sprc(yk_r)
```

###  Mosaic
```{r}
yk_m <- mosaic(yk_rsrc)
```

### Reproject to Equal area
```{r}
yk_ea = project(yk_m, "+proj=aea +lat_0=40 +lon_0=-96 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +type=crs", res=30)
```

### Save Raster Mosaic
```{r}
writeRaster(yk_ea, filename="../outputs/FieldDEM/FABDEM_EA_YK.tif", overwrite = TRUE)
```

## Alaska
### Make list of rasters
```{r}
ak_rlist <- list.files(path ="../data/DEMs/DEMFieldAK/",pattern = ".tif$",full.names = TRUE )
```

### Define as rasters
```{r}
ak_r <- lapply(ak_rlist, rast)
```

### Make a spatial raster collection
```{r}
ak_rsrc <- sprc(ak_r)
```

###  Mosaic
```{r}
ak_m <- mosaic(ak_rsrc)
```

### Reproject to Equal area
```{r}
ak_ea = project(ak_m, "+proj=aea +lat_0=40 +lon_0=-96 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +type=crs", res=30)
```

### Save Raster Mosaic
```{r}
writeRaster(ak_ea, filename="../outputs/FieldDEM/FABDEM_EA_AK.tif", overwrite = TRUE)
```

## NWT
### Make list of rasters
```{r}
nwt_rlist <- list.files(path ="../data/DEMs/DEMFieldNWT/",pattern = ".tif$",full.names = TRUE )
nwt_rlist
```

## Define as rasters
```{r}
nwt_r <- lapply(nwt_rlist, rast)
```

## Make a spatial raster collection
```{r}
nwt_rsrc <- sprc(nwt_r)
```

###  Mosaic
```{r}
nwt_m <- mosaic(nwt_rsrc)
```

### Reproject to Equal area
```{r}
nwt_ea = project(nwt_m, "+proj=aea +lat_0=40 +lon_0=-96 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +type=crs", res=30)
```

### Save Raster Mosaic
```{r}
writeRaster(nwt_ea, filename="../outputs/FieldDEM/FABDEM_EA_NWT.tif", overwrite = TRUE)
```

## SK
### Make list of rasters
```{r}
sk_rlist <- list.files(path ="../data/DEMs/DEMFieldSK/",pattern = ".tif$",full.names = TRUE )
sk_rlist
```

## Define as rasters
```{r}
sk_r <- lapply(sk_rlist, rast)
```

### Make a spatial raster collection
```{r}
sk_rsrc <- sprc(sk_r)
```

###  Mosaic
```{r}
sk_m <- mosaic(sk_rsrc)
```

### Reproject to Equal area
```{r}
sk_ea = project(sk_m, "+proj=aea +lat_0=40 +lon_0=-96 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +type=crs", res=30)
```

### Save Raster Mosaic
```{r}
writeRaster(sk_ea, filename="../outputs/FieldDEM/FABDEM_EA_SK.tif", overwrite = TRUE)
```


# Small Subgroups
use group 2

## SS1
```{r}
r_ss1 = sk_r[c(1:2)]
```


#### Make a spatial raster collection
```{r}
ss1_rsrc <- sprc(r_ss1)
```

####  Mosaic
```{r}
ss1_m <- mosaic(ss1_rsrc)
```

#### Reproject to Equal area
```{r}
ss1_ea = project(ss1_m, "+proj=aea +lat_0=40 +lon_0=-96 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +type=crs", res=30)
```

#### Save Raster Mosaic
```{r eval=FALSE, include=FALSE}
writeRaster(ss1_ea, filename="../outputs/FieldDEM/FABDEM_EA_ss1.tif", overwrite=TRUE)
```


## SS2
Lat 55-56 long -98--97
```{r}
r_ss2 = sk_r[c(60:62, 85:87)]
```

#### Make a spatial raster collection
```{r}
ss2_rsrc <- sprc(r_ss2)
```

####  Mosaic
```{r}
ss2_m <- mosaic(ss2_rsrc)
```

#### Reproject to Equal area
```{r}
ss2_ea = project(ss2_m, "+proj=aea +lat_0=40 +lon_0=-96 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +type=crs", res=30)
```

#### Save Raster Mosaic
```{r eval=FALSE, include=FALSE}
writeRaster(ss2_ea, filename="../outputs/FieldDEM/FABDEM_EA_ss2.tif", overwrite=TRUE)
```

## SSBP1
Lat 55-58 long 112-108
```{r}
r_ssbp1 = sk_r[c(97:100, 120:123)]
```


#### Make a spatial raster collection
```{r}
ssbp1_rsrc <- sprc(r_ssbp1)
```

####  Mosaic
```{r}
ssbp1_m <- mosaic(ssbp1_rsrc)
```

#### Reproject to Equal area
```{r}
ssbp1_ea = project(ssbp1_m, "+proj=aea +lat_0=40 +lon_0=-96 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +type=crs", res=30)
```

#### Save Raster Mosaic
```{r eval=FALSE, include=FALSE}
writeRaster(ssbp1_ea, filename="../outputs/FieldDEM/FABDEM_EA_ssbp1.tif", overwrite=TRUE)
```


## SSBP 2
Lat 53-55, lon 104-108
```{r}
r_ssbp2 = sk_r[c(17:22, 42:47, 67:72, 92:97)]
```


#### Make a spatial raster collection
```{r}
ssbp2_rsrc <- sprc(r_ssbp2)
```

####  Mosaic
```{r}
ssbp2_m <- mosaic(ssbp2_rsrc)
```

#### Reproject to Equal area
```{r}
ssbp2_ea = project(ssbp2_m, "+proj=aea +lat_0=40 +lon_0=-96 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +type=crs", res=30)
```

#### Save Raster Mosaic
```{r eval=FALSE, include=FALSE}
writeRaster(ssbp2_ea, filename="../outputs/FieldDEM/FABDEM_EA_ssbp2.tif", overwrite=TRUE)
```

## TS1
Lat 62-64, lon 113
```{r}
r_ts1 = nwt_r[c(27:29, 39:41, 51:53)]
```


#### Make a spatial raster collection
```{r}
ts1_rsrc <- sprc(r_ts1)
```

####  Mosaic
```{r}
ts1_m <- mosaic(ts1_rsrc)
```

#### Reproject to Equal area
```{r}
ts1_ea = project(ts1_m, "+proj=aea +lat_0=40 +lon_0=-96 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +type=crs", res=30)
```

#### Save Raster Mosaic
```{r eval=FALSE, include=FALSE}
writeRaster(ts1_ea, filename="../outputs/FieldDEM/FABDEM_EA_ts1.tif", overwrite=TRUE)
```

## TSTP1

```{r}
r_tstp1 = nwt_r[c(55:56)]
```


#### Make a spatial raster collection
```{r}
tstp1_rsrc <- sprc(r_tstp1)
```

####  Mosaic
```{r}
tstp1_m <- mosaic(tstp1_rsrc)
```

#### Reproject to Equal area
```{r}
tstp1_ea = project(tstp1_m, "+proj=aea +lat_0=40 +lon_0=-96 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +type=crs", res=30)
```

#### Save Raster Mosaic
```{r eval=FALSE, include=FALSE}
writeRaster(tstp1_ea, filename="../outputs/FieldDEM/FABDEM_EA_tstp1.tif", overwrite=TRUE)
```

## TP1

```{r}
r_tp1 = nwt_r[c(8:12, 20:24)]
```


#### Make a spatial raster collection
```{r}
tp1_rsrc <- sprc(r_tp1)
```

####  Mosaic
```{r}
tp1_m <- mosaic(tp1_rsrc)
```

#### Reproject to Equal area
```{r}
tp1_ea = project(tp1_m, "+proj=aea +lat_0=40 +lon_0=-96 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +type=crs", res=30)
```

#### Save Raster Mosaic
```{r eval=FALSE, include=FALSE}
writeRaster(tp1_ea, filename="../outputs/FieldDEM/FABDEM_EA_tp1.tif", overwrite=TRUE)
```

## TP2
lat 61-62, lon 117-115
```{r}
r_tp2 = nwt_r[c(17:20, 29:32)]
```


#### Make a spatial raster collection
```{r}
tp2_rsrc <- sprc(r_tp2)
```

####  Mosaic
```{r}
tp2_m <- mosaic(tp2_rsrc)
```

#### Reproject to Equal area
```{r}
tp2_ea = project(tp2_m, "+proj=aea +lat_0=40 +lon_0=-96 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +type=crs", res=30)
```

#### Save Raster Mosaic
```{r eval=FALSE, include=FALSE}
writeRaster(tp2_ea, filename="../outputs/FieldDEM/FABDEM_EA_tp2.tif", overwrite=TRUE)
```

## TP3
Lat 60, lon 117-114
```{r}
r_tp3 = nwt_r[c(4:8, 16:20)]
```


#### Make a spatial raster collection
```{r}
tp3_rsrc <- sprc(r_tp3)
```

####  Mosaic
```{r}
tp3_m <- mosaic(tp3_rsrc)
```

#### Reproject to Equal area
```{r}
tp3_ea = project(tp3_m, "+proj=aea +lat_0=40 +lon_0=-96 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +type=crs", res=30)
```

#### Save Raster Mosaic
```{r eval=FALSE, include=FALSE}
writeRaster(tp3_ea, filename="../outputs/FieldDEM/FABDEM_EA_tp3.tif", overwrite=TRUE)
```