---
title: "FAB DEM Mosaic"
author: "Anna Talucci"
date: "2023-03-10"
output: html_document
---

# Overview

Combine DEM tiles for study areas

SK field sites latitude and longitude range from FAB DEM from Compernicus (bare earth)

Lat long range for SK
Latitude (N)
[1] 53.1911
[1] 57.3646

Longitude (W)
[1] -111.3801
[1] -88.612

Lat long range for NWT
Latitude (N)
[1] 60.2151
[1] 64.1714

Longitude (W)
[1] -121.0111
[1] -113.0163

# Packages 

```{r}
library(terra)
library(gdalUtilities)
library(sf)
```


# Data

## Points
```{r}
pts = st_read("../data/FieldPoints/Field1983-2016/SKPoints1983-2016.shp", "SKPoints1983-2016") 
```

```{r}
head(pts)
```

```{r}
pt_shield = pts %>% filter(ecoregion =="Softwood Shield") 
pt_plains = pts %>% filter(ecoregion =="Boreal Plains") 
```

## Look at 1st and last sk raster
```{r}
first<-rast("../data/DEMs/DEMFieldSK/N53W088_FABDEM_V1-0.tif")
last<-rast("../data/DEMs/DEMFieldSK/N57W112_FABDEM_V1-0.tif")
```

```{r}
first
```

```{r}
last
```

# Projections
```{r}
projection<-crs(last)
projection
```

# Masaic with Terra 

## Yukon 
### Make list of rasters
```{r}
yk_rlist <- list.files(path ="../data/DEMs/DEMFieldYK/",pattern = ".tif$",full.names = TRUE )
```

### Define as rasters
```{r}
yk_r <- lapply(yk_rlist,   rast)
```

###  Make a spatial raster collection
```{r}
yk_rsrc <- sprc(yk_r)
```

###  Mosaic
```{r}
yk_m <- mosaic(yk_rsrc)
```

### Reproject to Equal area
```{r}
yk_ea = project(yk_m, "+proj=aea +lat_0=40 +lon_0=-96 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +type=crs", res=30)
```

### Save Raster Mosaic
```{r eval=FALSE, include=FALSE}
writeRaster(yk_m, filename="../outputs/FieldDEM/FABDEM_EA_YK.tif")
```

## Alaska
### Make list of rasters
```{r}
ak_rlist <- list.files(path ="../data/DEMs/DEMFieldAK/",pattern = ".tif$",full.names = TRUE )
```

### Define as rasters
```{r}
ak_r <- lapply(ak_rlist, rast)
```

### Make a spatial raster collection
```{r}
ak_rsrc <- sprc(ak_r)
```

###  Mosaic
```{r}
ak_m <- mosaic(ak_rsrc)
```

### Reproject to Equal area
```{r}
ak_ea = project(ak_m, "+proj=aea +lat_0=40 +lon_0=-96 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +type=crs", res=30)
```

### Save Raster Mosaic
```{r eval=FALSE, include=FALSE}
writeRaster(ak_m, filename="../outputs/FieldDEM/FABDEM_EA_AK.tif")
```

## NWT
### Make list of rasters
```{r}
nwt_rlist <- list.files(path ="../data/DEMs/DEMFieldNWT/",pattern = ".tif$",full.names = TRUE )
```

## Define as rasters
```{r}
nwt_r <- lapply(nwt_rlist, rast)
```

## Make a spatial raster collection
```{r}
nwt_rsrc <- sprc(nwt_r)
```

###  Mosaic
```{r}
nwt_m <- mosaic(nwt_rsrc)
```

### Reproject to Equal area
```{r}
nwt_ea = project(nwt_m, "+proj=aea +lat_0=40 +lon_0=-96 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +type=crs", res=30)
```

### Save Raster Mosaic
```{r eval=FALSE, include=FALSE}
writeRaster(nwt_m, filename="../outputs/FieldDEM/FABDEM_EA_NWT.tif")
```

## Sk
### Make list of rasters
```{r}
sk_rlist <- list.files(path ="../data/DEMs/DEMFieldSK/",pattern = ".tif$",full.names = TRUE )
```

## Define as rasters
```{r}
sk_r <- lapply(sk_rlist, rast)
```

### Make a spatial raster collection
```{r}
sk_rsrc <- sprc(sk_r)
```

###  Mosaic
```{r}
sk_m <- mosaic(sk_rsrc)
```

### Reproject to Equal area
```{r}
sk_ea = project(sk_m, "+proj=aea +lat_0=40 +lon_0=-96 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +type=crs", res=30)
```

### Save Raster Mosaic
```{r eval=FALSE, include=FALSE}
writeRaster(sk_m, filename="../outputs/FieldDEM/FABDEM_EA_SK.tif")
```

# Plot DEM

```{r eval=FALSE, include=FALSE}
plot(sk_m)
plot(st_geometry(points), add=TRUE)
```

```{r eval=FALSE, include=FALSE}
plot(nwt_m)
plot(st_geometry(points), add=TRUE)
```

```{r eval=FALSE, include=FALSE}
plot(ak_m)
plot(st_geometry(points), add=TRUE)
```

```{r eval=FALSE, include=FALSE}
plot(yk_m)
plot(st_geometry(points), add=TRUE)
```
