---
title: "NWT Shield Field & Tagee Terrain"
author: "Anna Talucci"
date: '2022-06-23'
output: html_document
---

# Overview
Data inspection of Tagee Terrain variables
# Packages

```{r}
library(tidyverse)
library(cowplot)
```

# Data

```{r}
nwtfielddata = read.csv("../data/Field/nwt_shield.csv")
nwtterrain = read.csv("../data/TageeTest/NWTShieldTagee.csv")
arctic = read.csv("../data/TageeTest/NWTShieldArctic.csv")
tpi = read.csv("../data/TPI/NWTShieldFabDemTPI.csv")
```


```{r}
head(nwtfielddata)
head(nwtterrain)
head(arctic)
head(tpi)
```
# Field moisture class add
1=xeric, 2=subxeric, 3=subxeric to mesic, 4=mesic, 5=submesic, 6=subhygric

```{r}
field = df %>% 
  mutate(moistureClass = ifelse(moisture==1, "xeric", 
                                ifelse(moisture==2, "subxeric",
                                       ifelse(moisture==3, "subxeric-mesic",
                                              ifelse(moisture==4, "mesic", 
                                                     ifelse(moisture==5, "submesic", 
                                                            ifelse(moisture==6, "subhygric", "NA")))))))

```

```{r}
field$moistureClass <- factor(field$moistureClass, levels=c("xeric", "subxeric", "subxeric-mesic", "mesic", "submesic", "subhygric"))
```

# Data Organize
```{r}
terrain = nwtterrain %>% 
  dplyr::select(prjct_d, latitud, longitd, Aspect:VerticalCurvature) %>%
  dplyr::rename(project_id = prjct_d, latitude = latitud, longitude = longitd)

terrain
  
```
```{r}
tpi1 = tpi %>% 
  dplyr::select(prjct_d, latitud, longitd, ASPTR:TPI450, elevation) %>%
  dplyr::rename(project_id = prjct_d, latitude = latitud, longitude = longitd)

tpi1
  
```

```{r}
arcticDEM = arctic %>% 
  dplyr::select(prjct_d, latitud, longitd, Aspect:VerticalCurvature) %>%
  dplyr::rename(project_id = prjct_d, 
                latitude = latitud, 
                longitude = longitd, 
                ArcAspect =Aspect, 
                ArcEastness = Eastness, 
                ArcElevation = Elevation, 
                ArcGausCurv = GaussianCurvature, 
                ArcHillshade = Hillshade, 
                ArcHorizCurv = HorizontalCurvature, 
                ArcMaxCurv = MaximalCurvature, 
                ArcMeanCurv = MeanCurvature, 
                ArcMinCurv = MinimalCurvature, 
                ArcNorthness = Northness, 
                ArcShapeIndex = ShapeIndex, 
                ArcSlope = Slope, 
                ArcVertCurv = VerticalCurvature)

arcticDEM
  
```

```{r}
df = merge(terrain, field, by = c("project_id", "latitude", "longitude"))
```

```{r}
df_tpi = merge(tpi1, field, by = c("project_id", "latitude", "longitude"))
```
```{r}
df1 = merge(arcticDEM, field, by = c("project_id", "latitude", "longitude"))
```

```{r}
df2 = merge(arcticDEM, df, by = c("project_id", "latitude", "longitude"))
```

```{r}
head(df)
```

# Difference in elevation
```{r}
df2 %>% 
  dplyr::select(project_id, ArcElevation, Elevation, elevation) %>%
  filter(elevation > 0) %>%
  mutate(ArcField = elevation-ArcElevation) %>%
  mutate(FABField = elevation - Elevation) 

```

```{r}
df2 %>% 
  dplyr::select(project_id, ArcElevation, Elevation, elevation) %>%
  filter(elevation > 0) %>%
  mutate(ArcField = elevation-ArcElevation) %>%
  mutate(FABField = elevation - Elevation) %>%
   summarise(across(ArcField:FABField, list(min = min, max = max, mean = mean)))

```

### Remove outliers
NWT.sf.239
NWT.sf.63
```{r}
target = c("NWT.sf.239", "NWT.sf.63")
df2 %>% 
  dplyr::select(project_id, ArcElevation, Elevation, elevation) %>%
  filter(elevation > 0) %>%
  filter(!project_id %in% target) %>%
  mutate(ArcField = elevation-ArcElevation) %>%
  mutate(FABField = elevation - Elevation) %>%
   summarise(across(ArcField:FABField, list(min = min, max = max, mean = mean)))

```

# Visualize data
df is Terrain from FABDEM and field data
```{r}
head(df)
```



## Moisture classes vs Form Attributes

```{r}
meanCurv = df %>%  
  ggplot(., aes(x=moistureClass, y=MeanCurvature)) +
  geom_boxplot() +
  xlab("Field Moisture") +
  ylab("Mean Curvature") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))

meanCurv
```
```{r}
maxCurv = df %>%  
  ggplot(., aes(x=moistureClass, y=MaximalCurvature)) +
  geom_boxplot() +
  xlab("Field Moisture") +
  ylab("Max Curvature") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))

maxCurv
```

```{r}
minCurv = df %>%  
  ggplot(., aes(x=moistureClass, y=MinimalCurvature)) +
  geom_boxplot() +
  xlab("Field Moisture") +
  ylab("Min Curvature") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))

minCurv
```

```{r}
gausCurv = df %>%  
  ggplot(., aes(x=moistureClass, y=GaussianCurvature)) +
  geom_boxplot() +
  xlab("Field Moisture") +
  ylab("Gaussian Curvature") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))

gausCurv
```
### Combine form plots
```{r fig.height=5, fig.width=6}
formPlot = plot_grid(meanCurv, gausCurv, minCurv, maxCurv, labels = "auto")

formPlot
```

```{r}
ggsave("../figures/FieldMoistureDEMForm.png", width = 6, height = 5, units = "in")

```
## Moisture classes vs Flow Attributes
```{r}
hCurv = df %>%  
  ggplot(., aes(x=moistureClass, y=HorizontalCurvature)) +
  geom_boxplot() +
  xlab("Field Moisture") +
  ylab("Horizontal Curvature") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))

hCurv
```

```{r}
vCurv = df %>%  
  ggplot(., aes(x=moistureClass, y=VerticalCurvature)) +
  geom_boxplot() +
  xlab("Field Moisture") +
  ylab("Vertical Curvature") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))

vCurv
```

```{r}
si = df %>%  
  ggplot(., aes(x=moistureClass, y=ShapeIndex)) +
  geom_boxplot() +
  xlab("Field Moisture") +
  ylab("Shape Index") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))

si
```
### Combine Flow plots
```{r fig.height=5, fig.width=6}
plot_grid(hCurv, vCurv, si, labels = "auto")
```
```{r}
ggsave("../figures/FieldMoistureDEMFlow.png", width = 6, height = 5, units = "in")

```

## Eastness Northness
```{r}
east = df %>%  
  ggplot(., aes(x=moistureClass, y=Eastness)) +
  geom_boxplot() +
  xlab("Field Moisture") +
  ylab("Eastness") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))

east
```

```{r}
north = df_class %>%  
  ggplot(., aes(x=moistureClass, y=Northness)) +
  geom_boxplot() +
  xlab("Field Moisture") +
  ylab("Northness") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))

north
```
### Combine North and East 
```{r fig.height=3, fig.width=6}
plot_grid(east, north, labels = "auto")
```
```{r}
ggsave("../figures/AKFieldMoistureEastNorth.png", width = 6, height = 3, units = "in")

```
## TPI vs Form Attributes

```{r}
tpi_plot = df_tpi %>%  
  ggplot(., aes(x=moistureClass, y=TPI450)) +
  geom_boxplot() +
  xlab("Field Moisture") +
  ylab("TPI") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))

tpi_plot
```

# Other visualization
## Elevation
```{r}
df %>% filter(elevation > 0) %>% 
  ggplot(., aes(x=elevation, y=Elevation)) +
  geom_point() +
  xlab("Field Elevation") +
  ylab("DEM Elevation")
```


```{r}
df1 %>% filter(elevation > 0) %>% 
  ggplot(., aes(x=elevation, y=Elevation)) +
  geom_point() +
  xlab("Field Elevation") +
  ylab("DEM Elevation")
```

```{r}
df2 %>% filter(Elevation > 0) %>% 
  ggplot(., aes(x=ArcElevation, y=Elevation)) +
  geom_point() 
```

## Slope
```{r}
df %>% filter(slope > 0) %>% 
  ggplot(., aes(x=slope, y=Slope)) +
  geom_point() +
  xlab("Field slope") +
  ylab("DEM Slope")
```

```{r}
df1 %>% filter(slope > 0) %>% 
  ggplot(., aes(x=slope, y=Slope)) +
  geom_point() +
  xlab("Field slope") +
  ylab("DEM Slope")
```
## Aspect

```{r}
df %>% filter(aspect > 0) %>% 
  ggplot(., aes(x=aspect, y=Aspect)) +
  geom_point() +
  xlab("Field aspect") +
  ylab("DEM Aspect")
```

## Prop SOL combusted vs. Vertical curvature
```{r}
df %>% filter(prop_sol_combusted > 0) %>% 
  ggplot(., aes(x=prop_sol_combusted, y=VerticalCurvature)) +
  geom_point() 
```

```{r}
df %>% filter(prop_sol_combusted > 0) %>% 
  ggplot(., aes(x=prop_sol_combusted, y=Slope)) +
  geom_point() 
```

```{r}
df %>% filter(prop_sol_combusted > 0) %>% 
  ggplot(., aes(x=prop_sol_combusted, y=ShapeIndex)) +
  geom_point() 
```

```{r}
df %>% filter(prop_sol_combusted > 0) %>% 
  ggplot(., aes(x=prop_sol_combusted, y=Northness)) +
  geom_point() 
```

```{r}
df %>% filter(prop_sol_combusted > 0) %>% 
  ggplot(., aes(x=prop_sol_combusted, y=MinimalCurvature)) +
  geom_point() 
```

```{r}
df %>% filter(prop_sol_combusted > 0) %>% 
  ggplot(., aes(x=prop_sol_combusted, y=MeanCurvature)) +
  geom_point() 
```

```{r}
df %>% filter(prop_sol_combusted > 0) %>% 
  ggplot(., aes(x=prop_sol_combusted, y=MaximalCurvature)) +
  geom_point() 
```

```{r}
df %>% filter(prop_sol_combusted > 0) %>% 
  ggplot(., aes(x=prop_sol_combusted, y=HorizontalCurvature)) +
  geom_point() 
```

```{r}
df %>% filter(prop_sol_combusted > 0) %>% 
  ggplot(., aes(x=prop_sol_combusted, y=Hillshade)) +
  geom_point() 
```

```{r}
df %>% filter(prop_sol_combusted > 0) %>% 
  ggplot(., aes(x=prop_sol_combusted, y=GaussianCurvature)) +
  geom_point() 
```

```{r}
df %>% filter(prop_sol_combusted > 0) %>% 
  ggplot(., aes(x=prop_sol_combusted, y=Elevation)) +
  geom_point() 
```

```{r}
df %>% filter(prop_sol_combusted > 0) %>% 
  ggplot(., aes(x=prop_sol_combusted, y=Eastness)) +
  geom_point() 
```

```{r}
df %>% filter(prop_sol_combusted > 0) %>% 
  ggplot(., aes(x=prop_sol_combusted, y=Aspect)) +
  geom_point() 
```