---
title: "One Fire Figures"
author: "Anna Talucci"
date: "2023-03-06"
output: html_document
---


# Overview

plot points

# Packages 

```{r}
library(tidyverse)
```

# Data

## Saga

```{r}
saga = read.csv("../data/PointTerrain/extractTerrainSaga.csv")
```

## Terra
```{r}
terra = read.csv("../data/PointTerrain/extractTerrainTerra.csv")
```

```{r}
tagee = read.csv("../data/PointTerrain/NWT1FireFABDEM.csv")
```

## Field
```{r}
field = read.csv("../data/FieldCSV/Field1983-2016/nwt_field.csv")
```

# Look at data

```{r}
head(saga)
head(terra)
head(tagee)
head(field)
```

# Join field and terrain data
```{r}
unique(terra$project_id)
```

```{r}
id_list = c("NWT.sf.102", "NWT.sf.103", "NWT.sf.138", "NWT.sf.139", "NWT.sf.140", "NWT.sf.141", "NWT.sf.142", "NWT.sf.143", "NWT.sf.144", "NWT.sf.145", "NWT.sf.146", "NWT.sf.147", "NWT.sf.148", "NWT.sf.149", "NWT.sf.150", "NWT.sf.151", "NWT.sf.152", "NWT.sf.153", "NWT.sf.154", "NWT.sf.155", "NWT.sf.156", "NWT.sf.157", "NWT.sf.158", "NWT.sf.159", "NWT.sf.160", "NWT.sf.161")
```

## Field + SAGA
```{r}
(
  field_saga = field %>% 
    dplyr::select(project_id, latitude, longitude, moisture) %>%
    dplyr::filter(project_id %in% id_list) %>%
    left_join(., saga, by = "project_id") 
)
```
```{r}

unique(field$moisture)
```
## Field + Terra
```{r}
(
  field_terra = field %>% 
    dplyr::select(project_id, latitude, longitude, moisture) %>%
    dplyr::filter(project_id %in% id_list) %>%
    left_join(., terra, by = "project_id") %>%
    mutate(soil = ifelse(moisture ==1, "xeric",
                                     ifelse(moisture == 2, "subxeric",
                                            ifelse(moisture == 3, "subxeric-mesic",
                                                   ifelse(moisture == 4, "mesic",
                                                          ifelse(moisture == 5, "mesic-subhygric",
                                                   ifelse(moisture == 6, "subhygric", "NA")))))))
)
```

## Field + TAGEE
```{r}
(
  tagee1 = tagee %>% 
    rename("project_id"= "prjct_d") %>%
    select(-system.index, -.geo)
)
```

```{r}
(
  field_tagee = field %>% 
    dplyr::select(project_id, latitude, longitude, moisture) %>%
    dplyr::filter(project_id %in% id_list) %>%
    left_join(., tagee1, by = "project_id") 
)
```
# Graphs

## SAGA 

### SAGA Aspect
```{r}
(
  p1 = ggplot(data = field_saga, aes(x=as.character(moisture), y=aspect)) +
    geom_boxplot() +
    labs(x="soil moisture", 
         y="aspect (degrees)",
         subtitle = "SAGA Aspect")
  
)
```

```{r}
ggsave("../figures/Boxplots/aspect.jpeg", plot = p1,  dpi = 300)
```

### SAGA ccros
```{r}
(
  p2 = ggplot(data = field_saga, aes(x=as.character(moisture), y=ccros)) +
    geom_boxplot() +
    labs(x="soil moisture", 
         y="Cross sectional curvature",
         subtitle = "SAGA Cross sectional curvature")
  
)
```

```{r}
ggsave("../figures/Boxplots/ccros.jpeg", plot = p2,  dpi = 300)
```

### SAGA cgene

```{r}
(
  p3 = ggplot(data = field_saga, aes(x=as.character(moisture), y=cgene)) +
    geom_boxplot() +
    labs(x="soil moisture", 
         y="General Curvature", 
         subtitle = "SAGA General Curvature")
)
```

```{r}
ggsave("../figures/Boxplots/cgene.jpeg", plot = p3,  dpi = 300)
```

### SAGA clong

```{r}
(
  p4 = ggplot(data = field_saga, aes(x=as.character(moisture), y=clong)) +
    geom_boxplot() +
    labs(x="soil moisture", 
         y="Longitudinal Curvature", 
         subtitle = "SAGA Longitudinal Curvature")
)
```

```{r}
ggsave("../figures/Boxplots/clong.jpeg", plot = p4,  dpi = 300)
```

### SAGA cmaxi

```{r}
(
  p5 = ggplot(data = field_saga, aes(x=as.character(moisture), y=cmaxi)) +
    geom_boxplot() +
    labs(x="soil moisture", 
         y="Maximum Curvature", 
         subtitle = "SAGA Maximum Curvature")
)
```

```{r}
ggsave("../figures/Boxplots/cmaxi.jpeg", plot = p5,  dpi = 300)
```

### SAGA cmini
```{r}
(
  p6 = ggplot(data = field_saga, aes(x=as.character(moisture), y=cmini)) +
    geom_boxplot() +
    labs(x="soil moisture", 
         y="Minimum Curvature", 
         subtitle = "SAGA Minimum Curvature")
)
```

```{r}
ggsave("../figures/Boxplots/cmini.jpeg", plot = p6,  dpi = 300)
```

### SAGA cplan
```{r}
(
  p7 = ggplot(data = field_saga, aes(x=as.character(moisture), y=cplan)) +
    geom_boxplot() +
    labs(x="soil moisture", 
         y="Plan Curvature", 
         subtitle = "SAGA Plan Curvature")
)
```

```{r}
ggsave("../figures/Boxplots/cplan.jpeg", plot = p7,  dpi = 300)
```

### SAGA cprof

```{r}
(
  p8 = ggplot(data = field_saga, aes(x=as.character(moisture), y=cprof)) +
    geom_boxplot() +
    labs(x="soil moisture", 
         y="Profile Curvature", 
         subtitle = "SAGA Profile Curvature")
)
```

```{r}
ggsave("../figures/Boxplots/cprof.jpeg", plot = p8,  dpi = 300)
```

### SAGA croto

```{r}
(
  p9 = ggplot(data = field_saga, aes(x=as.character(moisture), y=croto)) +
    geom_boxplot() +
    labs(x="soil moisture", 
         y="Flow line Curvature", 
         subtitle = "SAGA flow line Curvature")
)
```

```{r}
ggsave("../figures/Boxplots/croto.jpeg", plot = p9,  dpi = 300)
```

### SAGA ctang

```{r}
(
  p10 = ggplot(data = field_saga, aes(x=as.character(moisture), y=ctang)) +
    geom_boxplot() +
    labs(x="soil moisture", 
         y="Tangential Curvature",
         subtitle = "SAGA Tangential Curvature")
)
```

```{r}
ggsave("../figures/Boxplots/ctang.jpeg", plot = p10,  dpi = 300)
```

### SAGA ctota

```{r}
(
  p11 = ggplot(data = field_saga, aes(x=as.character(moisture), y=ctota)) +
    geom_boxplot() +
    labs(x="soil moisture", 
         y="Total Curvature",
         subtitle = "SAGA Total Curvature")
)
```

```{r}
ggsave("../figures/Boxplots/ctota.jpeg", plot = p11,  dpi = 300)
```

### SAGA flowpath

```{r}
(
  p12 = ggplot(data = field_saga, aes(x=as.character(moisture), y=flowpath)) +
    geom_boxplot() +
    labs(x="soil moisture", 
         y="flowpath",
         subtitle = "SAGA flowpath")
)
```

```{r}
ggsave("../figures/Boxplots/flowpath.jpeg", plot = p12,  dpi = 300)
```

### SAGA slope

```{r}
(
  p13 = ggplot(data = field_saga, aes(x=as.character(moisture), y=slope)) +
    geom_boxplot() +
    labs(x="soil moisture", 
         y="Slope (radians)",
         subtitle = "SAGA slope")
)
```

```{r}
ggsave("../figures/Boxplots/slope.jpeg", plot = p13,  dpi = 300)
```

### SAGA SWIL

```{r}
(
  p14 = ggplot(data = field_saga, aes(x=as.character(moisture), y=SWIL1)) +
    geom_boxplot() +
    labs(x="soil moisture", 
         y="Topographic Wetness Index (local)",
         subtitle = "SAGA Wetness Index (Local)")
  
)
```
```{r}
ggsave("../figures/Boxplots/swil.jpeg", plot = p14,  dpi = 300)
```

### SAGA SWIC
```{r}
(
  p15 = ggplot(data = field_saga, aes(x=as.character(moisture), y=SWIC1)) +
    geom_boxplot() +
    labs(x="soil moisture", 
         y="Topographic Wetness Index (catchment)", 
         subtitle = "SAGA Wetness Index (Catchment)")
)
```

```{r}
ggsave("../figures/Boxplots/swic.jpeg", plot = p15,  dpi = 300)
```


## Terra metrics

### Terra Aspect
```{r}
(
  p16 = ggplot(data = field_terra, aes(x=as.character(moisture), y=aspect)) +
    geom_boxplot() +
    labs(x="soil moisture", 
         y="aspect (degrees)",
         subtitle = "Terra Aspect")
  
)
```

```{r}
ggsave("../figures/Boxplots/terraAspect.jpeg", plot = p16,  dpi = 300)
```

### Terra Flow dir

```{r}
(
  p17 = ggplot(data = field_terra, aes(x=as.character(moisture), y=flowdir)) +
    geom_boxplot() +
    labs(x="soil moisture", 
         y="Flow direction", 
         subtitle = "Terra Flow Direction")
)
```

```{r}
ggsave("../figures/Boxplots/TerraFlowDir.jpeg", plot = p17,  dpi = 300)
```

### Terra Roughness
```{r}
(
  p18 = ggplot(data = field_terra, aes(x=as.character(moisture), y=roughness)) +
    geom_boxplot() +
    labs(x="soil moisture", 
         y="Roughness",
         subtitle = "Terra roughness")
)
```

```{r}
ggsave("../figures/Boxplots/TerraRoughness.jpeg", plot = p18,  dpi = 300)
```



### Terra Slope
```{r}
(
  p19 = ggplot(data = field_terra, aes(x=as.character(moisture), y=slope)) +
    geom_boxplot() +
    labs(x="soil moisture", 
         y="Slope (radians)",
         subtitle = "Terra slope")
)
```

```{r}
ggsave("../figures/Boxplots/TerraSlope.jpeg", plot = p19,  dpi = 300)
```

### Terra TPI
```{r}
(
  p20 = ggplot(data = field_terra, aes(x=as.character(moisture), y=TPI)) +
    geom_boxplot() +
    labs(x="soil moisture", 
         y="Topographic Position Index", 
         subtitle = "Terra TPI")
)
```

```{r}
ggsave("../figures/Boxplots/TPI.jpeg", plot = p20,  dpi = 300)
```

### Terra TPI
```{r}
(
  p21 = ggplot(data = field_terra, aes(x=as.character(moisture), y=TRI)) +
    geom_boxplot() +
    labs(x="soil moisture", 
         y="Topographic Ruggedness Index", 
         subtitle = "Terra TRI")
)
```

```{r}
ggsave("../figures/Boxplots/TRI.jpeg", plot = p21,  dpi = 300)
```

## TAGEE Plots

```{r}
field_tagee
```

### Aspect
```{r}
(
  p22 = ggplot(data = field_tagee, aes(x=as.character(moisture), y=Aspect)) +
    geom_boxplot() +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    labs(x="soil moisture", 
         y="Aspect", 
         subtitle = "TAGEE Aspect")
)
```

```{r}
ggsave("../figures/Boxplots/TAGeeAspect.jpeg", plot = p22,  dpi = 300)
```

### Eastness
```{r}
(
  p22 = ggplot(data = field_tagee, aes(x=as.character(moisture), y=Aspect)) +
    geom_boxplot() +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    labs(x="soil moisture", 
         y="Aspect", 
         subtitle = "TAGEE Aspect")
)
```

```{r}
ggsave("../figures/Boxplots/TAGeeAspect.jpeg", plot = p22,  dpi = 300)
```

### GaussianCurvature

```{r}
(
  p23 = ggplot(data = field_tagee, aes(x=as.character(moisture), y=GaussianCurvature)) +
    geom_boxplot() +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    labs(x="Soil moisture", 
         y="Gaussian Curvature", 
         subtitle = "TAGEE Gaussian Curvature")
)
```

```{r}
ggsave("../figures/Boxplots/TAGeeGaussianCurvature.jpeg", plot = p23,  dpi = 300)
```

### HorizontalCurvature

```{r}
(
  p24 = ggplot(data = field_tagee, aes(x=as.character(moisture), y=HorizontalCurvature)) +
    geom_boxplot() +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    labs(x="Soil moisture", 
         y="Horizontal Curvature", 
         subtitle = "TAGEE Horizontal Curvature")
)
```

```{r}
ggsave("../figures/Boxplots/TAGeeHorizontalCurvature.jpeg", plot = p24,  dpi = 300)
```

### MaximalCurvature
```{r}
(
  p25 = ggplot(data = field_tagee, aes(x=as.character(moisture), y=MaximalCurvature)) +
    geom_boxplot() +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    labs(x="Soil moisture", 
         y="Maximal Curvature", 
         subtitle = "TAGEE Maximal Curvature")
)
```

```{r}
ggsave("../figures/Boxplots/TAGeeMaximalCurvature.jpeg", plot = p25,  dpi = 300)
```

### MeanCurvature
```{r}
(
  p26 = ggplot(data = field_tagee, aes(x=as.character(moisture), y=MeanCurvature)) +
    geom_boxplot() +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    labs(x="Soil moisture", 
         y="Mean Curvature", 
         subtitle = "TAGEE Mean Curvature")
)
```

```{r}
ggsave("../figures/Boxplots/TAGeeMeanCurvature.jpeg", plot = p26,  dpi = 300)
```

### MinimalCurvature
```{r}
(
  p27 = ggplot(data = field_tagee, aes(x=as.character(moisture), y=MinimalCurvature)) +
    geom_boxplot() +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    labs(x="Soil moisture", 
         y="Minimal Curvature", 
         subtitle = "TAGEE Minimal Curvature")
)
```

```{r}
ggsave("../figures/Boxplots/TAGeeMinimalCurvature.jpeg", plot = p27,  dpi = 300)
```

### Northness
```{r}
(
  p28 = ggplot(data = field_tagee, aes(x=as.character(moisture), y=Northness)) +
    geom_boxplot() +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    labs(x="Soil moisture", 
         y="Northness", 
         subtitle = "TAGEE Northness")
)
```

```{r}
ggsave("../figures/Boxplots/TAGeeNorthness.jpeg", plot = p28,  dpi = 300)
```

### ShapeIndex
```{r}
(
  p29 = ggplot(data = field_tagee, aes(x=as.character(moisture), y=ShapeIndex)) +
    geom_boxplot() +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    labs(x="Soil moisture", 
         y="Shape Index", 
         subtitle = "TAGEE Shape Index")
)
```

```{r}
ggsave("../figures/Boxplots/TAGeeShapeIndex.jpeg", plot = p29,  dpi = 300)
```

### Slope
```{r}
(
  p30 = ggplot(data = field_tagee, aes(x=as.character(moisture), y=Slope)) +
    geom_boxplot() +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    labs(x="Soil moisture", 
         y="Slope", 
         subtitle = "TAGEE Slope")
)
```

```{r}
ggsave("../figures/Boxplots/TAGeeSlope.jpeg", plot = p30,  dpi = 300)
```

### VerticalCurvature
```{r}
(
  p31 = ggplot(data = field_tagee, aes(x=as.character(moisture), y=VerticalCurvature)) +
    geom_boxplot() +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    labs(x="Soil moisture", 
         y="Vertical Curvature", 
         subtitle = "TAGEE Vertical Curvature")
)
```

```{r}
ggsave("../figures/Boxplots/TAGeeVerticalCurvature.jpeg", plot = p31,  dpi = 300)
```