---
title: "Terrain with RSaga Test"
author: "Anna Talucci"
date: '2022-06-27'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Overview


[Link to RSAGA Vignette](https://cran.r-project.org/web/packages/RSAGA/vignettes/RSAGA.html)

# Packages

```{r}
library(RSAGA)
```
#$ Define

```{r}
rsaga.path <-"/Library/Frameworks/R.framework/Versions/4.2/Resources/library/RSAGA"

```

```{r}
rsaga.path <-"/Users/annatalucci/saga-6.2.0/src/saga_core/saga_cmd"
```


```{r}
saga_cmd = "/Users/annatalucci/develop/saga-code/saga-gis/src/saga_core/saga_cmd/saga_cmd"
saga_modules = "/Users/annatalucci/develop/saga-code/saga-gis/cmake/modules"
```
/Applications/saga-6.2.0
/Users/annatalucci/saga-gis

rsaga.env(workspace = ".", cmd = ifelse(Sys.info()["sysname"] == "Windows",
  "saga_cmd.exe", "saga_cmd"), path, modules, version, cores,
  parallel = FALSE, check.libpath = TRUE, check.SAGA = TRUE,
  check.PATH = Sys.info()["sysname"] == "Windows", check.os.default = TRUE,
  os.default.path = rsaga.default.path(), lib.prefix)
  
```{r}
rsaga.env(workspace = ".", cmd = saga_cmd, path="/Users/annatalucci/develop/saga-code/saga-gis/src/saga_core/saga_cmd/saga_cmd", modules=saga_modules)
```
```{r}
rsaga.env(workspace = ".", cmd = "/usr/local/bin", path="/Users/annatalucci/develop/saga-code/saga-gis/", modules="/lib/saga")
```
# Set up RSAGA environment
Not rightt (Delete)
```{r}
myenv <- rsaga.env()
myenv
```
 env <- rsaga.env(path="C:/Program Files (x86)/SAGA-GIS-2-1-0")
```{r}
env <- rsaga.env(path=rsaga.path) 
```
```{r}
if (FALSE) {

# call if you do not have any idea if and where SAGA GIS is installed
# it will return a list with the selected and available SAGA installations
# it prepares the system for running the selected SAGA version via RSAGA or CLI
linkSAGA()

# overriding the default environment of rsaga.env call 

saga<-linkSAGA()
if (saga$exist) {
require(RSAGA)
RSAGA::rsaga.env(path = saga$installed$binDir[1],modules = saga$installed$moduleDir[1])
}
}
```

```{r}
rsaga.env(modules = saga$sagaModPath)
```

```{r}
rsaga.geoprocessor(lib = "ta_morphometry", module = "Slope, Aspect, Curvature",
                   param = list(ELEVATION = paste(getwd(),"/dem.sgrd", sep = ""), 
                                SLOPE = paste(getwd(),"/slope.sgrd", sep = "")),
                   env = env)
```


# Data